Accelerating the Computation of Geometric Constraints in Optimization

### 2019-12-12 report/paper.tex
All but timing data

\documentclass[11pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{bm}
\usepackage{ mathrsfs }
\usepackage{multirow}
\usepackage{subcaption}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[backend=bibtex]{biblatex}
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}
 \usepackage[top=3cm, bottom=2cm, left=1.9cm, right=1.9cm]{geometry}

@@

\qquad During the course of my research, I identified a mathematical formulation for a geometric constraint which meets these requirements.
We begin with triangulated representations of aircraft outer surface $A$ and an inner object $B$ to pack inside it, as pictured in Figure~\ref{fig:schematic}.
$A$ and $B$ are each represented as lists of vertices $V_0$, $V_1$, $V_2$ of dimension 3 by $m$ or $n$ (the size of each mesh).

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.45\linewidth]{figures/schematic}
  % \vspace{-30pt}
  \caption{A section view of an object $B$ inside wing $A$ and the minimum distance $d_\text{min}$ between them}
  \label{fig:schematic}
\end{figure}

\qquad When one object encloses another, the minimum distance $d_\text{min}$ between them is greater than zero by some margin.
Therefore, a first approach to a geometric constraint might involve computing $d_\text{min,AB} \geq 0 + \text{tol}$.
We can compute $d_\text{min}$ between two triangulated surfaces by computing the minimum distance between each individual pair of triangles.
The minimum distance between a pair of triangles can be found by a total of fifteen primitive tests between the vertices: six point-triangle tests, and nine line-line tests (Figure~\ref{fig:primitives}). % TODO cite ericson

\begin{equation}
  \label{eq:dmin}
  d_\text{min,AB} = \text{min}(d_{\text{min},ij}) \text{ for each triangle } i, \, j \text{ in surfaces } A, \, B
\end{equation}

@@

where $\textbf{x}$ is a vector of design variables,
$d_{ij}(\textbf{x})$ is the pairwise distance between the $i$th facet of $A$ and $j$th facet of $B$,
$d_{min}(\textbf{x})$ is the minimum distance between $A$ and $B$ at the current design point, and
$\rho$ is a user-controllable constant.

@@

\section{Benchmarking Case Description}
\qquad I wanted to isolate performance metrics to the geometry code, yet test the code in a setting representative of an optimization run, so I generated an artificial test problem.
Consider a blended wing body (BWB) aircraft, as pictured in Figure~\ref{fig:bwb-alone}.
We might optimize the shape of this aircraft to minimize drag.
Aircraft also need to hold systems components (such as actuators and hydraulic pumps).
I created a notional football-shaped geometry to represent a generic system component to be packed optimally into the wing and placed it into the right wing root, as pictured in Figure~\ref{fig:bwb-blob}.
We can then compute Equation~\ref{ks_geom} between the aircraft outer shape and the football-shaped inner component to see whether the current layout is feasible.

@@

\section{Baseline Code Development and Verification}
\qquad Because this code will be used to produce published research results, I need to ensure the code is not only fast, but also accurate.
I developed the code in the following general steps:
\begin{itemize}
  \item Writing line-line and point-triangle test primitive subroutines
  \item Algorithmic differentiation of the geometric primitives
  \item Writing the serial KS function subroutine (implementing Equation~\ref{ks_geom})
  \item Creating the Python-Fortran interface
  \item Unit testing of the geometric primitives and KS function
  \item Parallelizing the KS function subroutine
  \item Verification of the derivative output using the complex step methods
\end{itemize}

@@

\begin{itemize}
  \item $A_1$, $B_1$, $C_1$: lists of vertices comprising the $m$ triangles of the outer surface
  \item $A_2$, $B_2$, $C_2$: lists of vertices comprising the $n$ triangles of the inner object surface
  \item $d_\text{min,current}$: the minimum distance between the two surfaces at the current design point (this is used to normalize the calculation which improves numerical conditioning)
  \item $\rho$: a user-defined constant which defines how tight the objects can fit next to each other 
\end{itemize}

@@

@@

\begin{equation}
  \frac{dKS}{d\textbf{A}_1} \, \, \, \, \, \, \frac{dKS}{d\textbf{B}_1} \, \, \, \, \, \, \frac{dKS}{d\textbf{C}_1} 
\end{equation}

@@

\begin{equation}
  \frac{dKS}{d\textbf{A}_2} \, \, \, \, \, \, \frac{dKS}{d\textbf{B}_2} \, \, \, \, \, \, \frac{dKS}{d\textbf{C}_2} 
\end{equation}

Differentiating top-level code, particularly when it involves dynamically-allocated arrays or MPI calls, can be very inefficient.
Therefore, I differentiated Equation~\ref{ks_geom} by hand using the AD results for the geometric primitives.
% TODO write down the expression
Since the entries of the derivatives depend on both local information as well as the global summation across all the facet pairs, the overall computation is not embarassingly parallel.
However, the amount of communication required is fairly low (a single partial sum is Allgathered from all processes) in between two separate double $ij$ loops.
There is also no stencil-type calculation where offsets from $ij$ are used, meaning that an owner-computes approach will be fine.

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{bm}
\usepackage{ mathrsfs }
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{relsize}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[backend=bibtex]{biblatex}
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}
 \usepackage[top=3cm, bottom=2cm, left=1.9cm, right=1.9cm]{geometry}

@@

\qquad During the course of my research, I identified a mathematical formulation for a geometric constraint which meets these requirements.
We begin with triangulated representations of aircraft outer surface $r$ and an inner object $s$ to pack inside it, as pictured in Figure~\ref{fig:schematic}.
$r$ and $s$ are each represented as lists of vertices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$ of dimension 3 by $m$ or $n$ (the size of each mesh).

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.45\linewidth]{figures/schematic}
  % \vspace{-30pt}
  \caption{A section view of an object $s$ inside wing $r$ and the minimum distance $d_\text{min}$ between them}
  \label{fig:schematic}
\end{figure}

\qquad When one object encloses another, the minimum distance $d_\text{min}$ between them is greater than zero by some margin.
Therefore, a first approach to a geometric constraint might involve computing $d_\text{min,rs} \geq 0 + \text{tol}$.
We can compute $d_\text{min}$ between two triangulated surfaces by computing the minimum distance between each individual pair of triangles.
The minimum distance between a pair of triangles can be found by a total of fifteen primitive tests between the vertices: six point-triangle tests, and nine line-line tests (Figure~\ref{fig:primitives}). % TODO cite ericson

\begin{equation}
  \label{eq:dmin}
  d_\text{min,rs} = \text{min}(d_{\text{min},ij}) \text{ for each triangle } i, \, j \text{ in surfaces } r, \, s
\end{equation}

@@

where $\textbf{x}$ is a vector of design variables,
$d_{ij}(\textbf{x})$ is the pairwise distance between the $i$th facet of $r$ and $j$th facet of $s$,
$d_{min}(\textbf{x})$ is the minimum distance between $r$ and $s$ at the current design point, and
$\rho$ is a user-controllable constant.
Strictly speaking, $d_{ij}$ is a function of the surface mesh points of $r$ and $s$, not the design variables $\textbf{x}$ directly.

@@

\section{Benchmarking Case Description}
\label{sec:benchmark}
\qquad I wanted to isolate performance metrics to the geometry code, yet test the code in a setting representative of an optimization run, so I generated an artificial test problem.
Consider a blended wing body (BWB) aircraft, as pictured in Figure~\ref{fig:bwb-alone}.
We might optimize the shape of this aircraft to minimize drag.
Aircraft also need to hold systems components (such as actuators and hydraulic pumps).
I created a notional football-shaped geometry to represent a generic system component to be packed optimally into the wing and placed it into the right wing root, as pictured in Figure~\ref{fig:bwb-blob}.
We can then compute Equation~\ref{ks_geom} between the aircraft outer shape $r$ and the football-shaped inner component $s$ to see whether the current layout is feasible.

@@

\section{Baseline Code Development and Verification}
\qquad Because this code will be used to produce published research results, I need to ensure the code is not only fast, but also accurate.
I developed the code in the following general steps:
\begin{itemize}
  \item Writing line-line and point-triangle test primitive subroutines
  \item Algorithmic differentiation of the geometric primitives
  \item Writing the serial KS function subroutine (implementing Equation~\ref{ks_geom})
  \item Creating the Python-Fortran interface
  \item Unit testing of the geometric primitives and KS function
  \item Parallelizing the KS function subroutine
\end{itemize}

@@

\begin{itemize}
  \item $A_r$, $B_r$, $C_r$: lists of vertices comprising the $m$ triangles of the outer surface
  \item $A_s$, $B_s$, $C_s$: lists of vertices comprising the $n$ triangles of the inner object surface
  \item $d_\text{min,current}$: the minimum distance between the two surfaces at the current design point (this is used to normalize the calculation which improves numerical conditioning)
  \item $\rho$: a user-defined constant which defines how tight the objects can fit next to each other
\end{itemize}

@@

The major advantage that this Fortran implementation has over Tensorflow is data reuse.
Tensorflow computes each array operation in a pairwise fashion sequentially.
Every entry in each array is read one time per array operation, and one write is performed per array operation.
This should result in a bad compute-to-memory access ratio.
In the Fortran implementation, each pair of triangles is read from the global arrays only one time.
Subsequently, all the primitive tests and summation is performed on local copies which should easily fit in the L1 cache.
This should result in a major speedup over the Tensorflow implementation by itself.

I was careful to ensure sequential memory access by arranging the array order correctly.
Fortran uses column-major order, so I used the spatial dimensions $x,y,z$ as the first array dimension, and triangle count $i,j$ as the second dimension.
This results in coalesced memory access when individual vertices are read from the global arrays.
However, for the purposes of visualization in this paper, I illustrate the transpose of the matrix, with each row comprising a triangle.

@@

\begin{equation}
  \frac{dKS}{d\textbf{A}_r} \, \, \, \, \, \, \frac{dKS}{d\textbf{B}_r} \, \, \, \, \, \, \frac{dKS}{d\textbf{C}_r}
\end{equation}

@@

\begin{equation}
  \frac{dKS}{d\textbf{A}_s} \, \, \, \, \, \, \frac{dKS}{d\textbf{B}_s} \, \, \, \, \, \, \frac{dKS}{d\textbf{C}_s}
\end{equation}

These derivatives are required in order to compute the total derivative of the KS function with respect to the design variables.
Recall that Equation~\ref{ks_geom} depends on the surface mesh vertices $A$, $B$, and $C$ of objects $r$ and $s$.
Applying the chain rule, we have:

\begin{equation}
  \frac{dKS}{d\textbf{x}} = \frac{dKS}{d\textbf{A}_r(\textbf{x})} \frac{d\textbf{A}_r(\textbf{x})}{d\textbf{x}} +
                            \frac{dKS}{d\textbf{B}_r} \frac{d\textbf{B}_r}{d\textbf{x}} +
                            \frac{dKS}{d\textbf{C}_r} \frac{d\textbf{C}_r}{d\textbf{x}} +
                            \frac{dKS}{d\textbf{A}_s} \frac{d\textbf{A}_s}{d\textbf{x}} +
                            \frac{dKS}{d\textbf{B}_s} \frac{d\textbf{B}_s}{d\textbf{x}} +
                            \frac{dKS}{d\textbf{C}_s} \frac{d\textbf{C}_s}{d\textbf{x}}
\end{equation}
We have a separate Python tool which provides the design variable sensititivies $d\textbf{A,B,C}/d\textbf{x}$.

\qquad Differentiating top-level code, particularly when it involves dynamically-allocated arrays or MPI calls, can be very inefficient.
Therefore, I differentiated Equation~\ref{ks_geom} by hand, obtaining:

\begin{equation}
  \frac{dKS}{d\textbf{A}_r} = -\frac{\mathlarger{\sum_{i,j=1}^{m,n} \frac{d\,d_{ij}}{d\textbf{A}_r}e^{\rho\big(d_\text{min}-d_{ij}\big)}}}
  {\mathlarger{\sum_{i,j=1}^{m,n} e^{\rho\big(d_\text{min}-d_{ij}\big)}}}
\end{equation}

and so on for the remaining 5 lists of input vertices.
$d\,d_{ij}/d\textbf{A}_r$ is computed using the AD version of the geometric primitives.

\qquad Note that, while $dKS/d\textbf{A}_r$ is a dense $m$ by 3 matrix, each pairwise update in the summation ($d\,d_{ij}/d\textbf{A}_r$) is sparse and affects at most 3 entries at a time.
Note also that the summation in the denominator is a global quantity, while the numerator is a local quantity specific to each facet pair $i$,$j$.
Since the entries of the derivatives depend on both local information as well as the global summation across all the facet pairs, the overall computation is not embarassingly parallel.
However, the amount of communication required is fairly low (a single partial sum is Allgathered from all processes) in between two separate double $ij$ loops.

\subsection{Fortran-Python interface}
\qquad The lab's optimization framework is Python-based.
Therefore, all geometry information fed into the Fortran code needs to be passed in from a Python process executed under MPI.
Normally, writing Python native interfaces is a royal pain, and in the past I have used the low-level Python-C API to do this.

\qquad A better way is to use the \texttt{f2py} interface generator.
\texttt{f2py} was developed as part of the \texttt{numpy} project and it is distributed with \texttt{numpy}.
It consists of a command-line interface which reads and compiles Fortran source and generates a \texttt{.so} shared object file which can be imported as a Python package.
The user can control the structure of the input and output arguments by writing an f2py ``signature'' file, which I did in this case.
F2py passes in numpy arrays by reference as native Fortran array pointers in the correct column-major memory layout.

\qquad The build process can be pretty involved, so I created a Makefile for the project.
The default ``make'' command line argument on Linux should successfully compile and test the entire project, assuming the proper dependencies are already installed.

\subsection{Testing and Verification}
\qquad A major benefit of the Python interface is that it is easy to create unit and integration tests.
As I developed the codebase in a bottom-up approach, I ensured that unit tests were written and passing before moving on.
First, I generated unit tests which cover every branch of the geometry primitives using simple configurations of triangles (\texttt{test\_primitives.py}).
Next, it is absolutely crucial to test the accuracy of AD derivatives, since Tapenade sometimes can be buggy and these types of errors can be difficult to detect in integration testing.

\qquad In order to verify derivatives, we use the \emph{complex step} method (CS).
The complex step method (Equation~\ref{eq:complex_step}) is conceptually similar to finite differencing, except that it is exactly accurate even when a very small step (on the order of machine $\epsilon$) is used.
This makes it suitable for testing the exact derivatives obtained via AD to high precision.

\begin{equation}
  \label{eq:complex_step}
  \frac{df(x)}{dx} = \frac{\text{Im}(f(x+ih))}{h}
\end{equation}

\qquad The drawback of the complex step method is that it requires that the code being tested support complex inputs.
Fortunately, our lab has developed a method for compiling complex versions of our Fortran codes.
We use a Python script to transform the base code into a complexified version.
The script changes data types and overloads certain functions so that they produce the correct control flow even with complex inputs.
I added this complex build to the Makefile and wrote unit tests verifying the derivatives of both the geometric primitives as well as the top-level KS function derivatives.
All the derivative outputs matched CS to a relative tolerance of $10^{-7}$, indicating that both the AD derivatives and the by-hand derivative assembly were correctly implemented.

\qquad Finally, I ported my previous integration tests from \texttt{geograd} over to this project and verified that the output values match the output values of my new code for known geometries.
They did match to a high degree of accuracy.

\subsection{Parallelizing the Baseline Code}
\qquad As a first cut, I parallelized the new Fortran code in the same way that I had parallelized \texttt{geograd}.
Here are the assumptions and requirements for the parallelization:
\begin{itemize}
  \item Assume each process has a full copy of the input meshes $r$ and $s$ when it is called (no scatter from root required)
  \item Each process must end up with a full copy of both the KS value and all the derivative arrays
  \item The $p$ processors will be provisioned such that $p >> m, n$
\end{itemize}
We divide up the problem along the $r$ mesh only.
Each processor is given a range of rows in the $r$ mesh arrays to compute against all of the $s$ triangles.
Figure~\ref{fig:parallel} shows the parallelized arrangement.
First, an owner-computes approach is used to compute the summation of the KS function.
Each process recieves the summation value via an allreduce.
If analysis is being performed without the need for derivatives, the computation is done at this point.
If not, the derivatives are computed in an owner-computes fashion.
Since the processors ``share jurisdiction'' over the $s$ mesh, an MPI Allreduce summation is used to combine local copies of the $s$ derivatives into a global array.
The $r$ mesh is simply concatenated and sent to all using the MPI Allgather subroutine.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.95\linewidth]{figures/parallelization}
  \caption{The problem is parallelized by dividing up the larger array and distributing its computation evenly across the processors}
  \label{fig:parallel}
\end{figure}

\subsection{Timing the Baseline}
I ran the \texttt{geograd} (Tensorflow-based) implementation and my new Fortran implementation on the benchmark problem described in Section~\ref{sec:benchmark} using 4 to 48 cores of a compute node on the TACC Stampede2 cluster.
Unless otherwise specified in the report, I give timings and speedups for the 48-core case.
The Tensorflow-based benchmark took 20s to run analysis only, and 38s for derivatives.
My new Fortran-based benchmark took 0.371s for analysis only (\textbf{53x} speedup), and 1.93s for derivatives (\textbf{19x} speedup).
These were extremely promising results, and I had not yet implemented any of the algorithm improvements.

\section{Algorithm Improvements}
Because Tensorflow does not support control flow (at least, not in a form which reduces computation for unused branches), there is great opportunity to gain speed by improving the algorithm.
In this section I describe the improvements and report speedup relative to the previous iteration (not cumulative versus the original Tensorflow implementation).

\subsection{Minimum instead of Sum of the 15 Triangle Tests}
Recall the 6 point-triangle and 9 line-line tests performed for each pair $i,j$ of triangles, as shown in Figure~\ref{fig:primitives}.
In Tensorflow, there is no computational advantage to taking the minimum value of the 15 pairwise primitive tests, so I sum the KS results instead.
However, in Fortran, I can eliminate 14 of the 15 derivative calls by taking the minimum instead of the sum.
I added a case control flow structure to only run the derivative subroutine for the most critical primitive.
This had only a modest effect on the analysis-only benchmark (\textbf{1.1x} speedup), but a large effect on the derivatives benchmark (\textbf{3.93x} speedup).
This optimization remains an exactly correct expression of Equation~\ref{ks_geom}.

\subsection{Bounding Box Testing}
If a pair of triangles is far away from each other, it is possible to prove cheaply that their interaction is not important.
We can accomplish this through \emph{bounding box} testing.
Let's draw an axis-aligned bounding box around the inner object $s$ as pictured in Figure~\ref{fig:bb-test}.
Let us also define some tolerance value (say, the maximum dimension of $s$ in any dimension).
If the bounding box around triangle $j$ is more than $tol$ away from the bounding box of $s$, then we can guarantee that the minimum distance between them is at least $tol$.
We can then replace a potentially large number of $d_{ij}$ computations with $d_{ij}=tol$.

Computing bounding box tests is much cheaper than computing $d_{ij}$ using the subroutines.
The bounding box test is simply several min/max operations on each triangle $j$, plus a few floating point comparisons.
Since aircraft geometry predominantly varies in the wingspan direction, we can exclude a huge number of triangles with just one or two comparisons (by placing the $x$ axis tests first in the sequence).

I implemented the bounding box test using the heuristic $tol$ setting of $max(x_{max}-x_{min},\,y_{max}-y_{min},\,z_{max}-z_{min}$ and re-ran the benchmark cases.
The derivative benchmark gained an additional \textbf{3.4x} speedup compared to the previous optimization.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/bb_test}
  \caption{Bounding box tests can quickly exclude obviously unimportant facets from needing expensive computation}
  \label{fig:bb-test}
\end{figure}

\section{Dynamic Load Balancing}
While the baseline Fortran implementation and the ``min of fifteen'' optimization had good load balancing (utilization above 95\% with 4 processors; above 65\% with 48 processors), the bounding box test absolutely ruined the load balancing.
The reason for this is spatial correlation in the lists of mesh vertices.
Consider the aircraft geometry pictured above.
A mesh representation might include all of the ``left wing'' triangles in the first quarter of the list, or it may be completely random (there are no guarantees).
A bounding box test excludes triangles that are far from the present position of the object $s$.
Therefore, if $s$ is in the right wing, the processor which is assigned all of the left wing facets may have zero triangles to compute.
Furthermore, as $s$ and $r$ deform and move during optimization, the load imbalance will change from processor to processor.

I measured this using the benchmarking case.
After implementing the bounding box test, my processor utilization across 48 MPI processes decreased from the high 60\% range to less than 15\%.
Examining the problem further, I found that one or two processors would have basically zero runtime, while the others were fully loaded.
I verified that these low-runtime processes had most or all of their triangles excluded from expensive tests by the bounding box.
Below, I will describe two approaches I used to solve the problem.

\subsection{Global Load Balancing}
Due to the dynamic nature of the load balancing issue, the load balancing step needs to be done on every function call.
As a first cut, I decided to treat the bounding box tests as negligible in cost and simply smear all of the ``active'' triangles (the ones passing the bounding-box test and requiring more expensive tests) evenly across the processors sequentially.
Briefly, the method is as follows:
\begin{itemize}
\item First, divide up all the triangles evenly across the processors
\item Compute bounding box tests and place a boolean into a local vector indicating whether it is active or inactive
\item Allgather the bounding box test results into a global vector on each processor
\item Compute the sum of all active triangles in the global vector
\item Compute a scan on the global vector to find the global indices $i$ of the triangles in $r$ across which the problem will be split for load balancing
\item Divide the triangles up across the new split indices
\end{itemize}
The structure of the problem remains as pictured in Figure~\ref{fig:parallel}, except that each processor will now have an unequal number of triangles to compute.
I chose to ignore the potential issue of some processors having more inactive (cheap) triangles to compute than others.
This keeps the array split indices limited in size and the split chunks contiguous in memory, which simplifies the collective operations required to get the derivatives assembled at the end.

This global load balancing method was very effective.
Processor utilization improved from about 11\% to 65\% (similar to the levels seen before implementing the bounding box tests).
The remaining idleness is attributable to some point-triangle or line-line tests being more expensive to compute than others (early exits, etc.), or to OS interrupts.
If the number of triangles per processor is high enough, load balancing improves to about 95\% (as in weak-scaling benchmark results).
With the load balancing in place, derivatives gained another \textbf{2.6x} speedup versus the unbalanced bounding box benchmark.
However, I noted that weak scaling seemed to suffer somewhat for this iteration.

After conducting some detailed profiling, I noted that the load balancing step was increasing in time as the number of triangles increased.
The reason was the MPI Allgather operation I used to construct the global load balancing vector.
My reasoning for this was to save bounding box test results so they wouldn't need to be recomputed later in the main loop.
However, it was clear that this would potentially cause poor scaling for larger problems.

\subsection{Distributed Load Balancing}
In order to eliminate the Allgather operation from the load balancing step, two changes were required.
First, I had to develop a distributed scan methodology to determine where the load balancing break indices would be located, without gathering a global vector of bounding box test results.
I was able to do this using an Allreduce operation with only as many values as processors, eliminating the weak scaling issue.
The second change was to insert the bounding box tests back into the main KS computation loop.
This resulted in doing some redundant bounding box tests, but they are so cheap that it barely matters.

I ran the benchmark for this distributed load balancing variant and found that the processor utilization remained equally high, and that the poor weak scaling of the load balancing step had disappeared.
Distributing the load balancing accounts for only about a \textbf{1.1x} speedup compared to the global load balancing, but it eliminates a sub-optimal scaling property that could come back to bite me in the future when working with larger problems.
